---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# govinfoR

<!-- badges: start -->
<!-- badges: end -->

`govinfoR` offers an easy way to access data provided by the [United States Government Publishing Office (GPO) GovInfo API](https://api.govinfo.gov) in R. It's currently in early development, but functions for all GET endpoints are available. The API's `search` endpoint, which as of this writing is in Public Preview, is outside the scope of this package at present.

## Installation

You can install the stable version of `govinfoR` from [CRAN](https://cran.r-project.org/package=govinfoR) with:

``` r
install.packages("govinfoR")
```

You can install the development version of `govinfoR` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("blackerby/govinfoR")
```

## Examples

This first example loads the package, sets the API key (gotten from the environment), and gets metadata about all 39 GovInfo collections.

```{r example_1}
library(govinfoR)

set_govinfo_key(get_govinfo_key())

gpo_collections()
```

The following example demonstrates getting all records in the `BILLS` collection since midnight yesterday.

> The package provides three simple helpers to make it easier to specify dates as arguments to functions (`yesterday()`, `today()`, and `tomorrow()`)

```{r example_2}
gpo_collections(collection = "BILLS", start_date = yesterday())
```

Examples of the use of other package functions are in the documentation.
